Environmental and geographic variables are effective surrogates for genetic variation in conservation planning

### 2017-08-06 code/rmarkdown/supporting_information.Rmd
updated si

```{r, echo=FALSE, include=FALSE}
plot.spp.spaces <- function(i) {
  ## prepare data
  # get vector of adaptive and neutral column names
  adapt.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_adaptive_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  neutral.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_neutral_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  env.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_env_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  # skip species if not used in analysis
  curr.FPLY <- grid.FPLY %>%
    select(one_of(adapt.col, neutral.col, env.col), group, long, lat) %>%
    mutate_each(funs(unname), one_of(adapt.col, neutral.col, env.col)) %>%
    filter(!is.na(.[[1]])) %>%
    gather(d, value, contains('adaptive'), contains('neutral'), contains('env')) %>%
    mutate(d=as.character(d)) %>%
    mutate(d=gsub(paste0(unique(spp.samples.DF$species)[i], '_'), '', d, fixed=TRUE)) %>%
    mutate(d=gsub('_', ' ', d, fixed=TRUE)) %>%
    mutate(d=gsub('env', 'environmental', d, fixed=TRUE))
  for (j in seq_len(max(length(adapt.col),length(neutral.col),length(env.col))))
    curr.FPLY$d <- gsub(paste0('d', as.character(j)), paste0('(', j, ')'), curr.FPLY$d, fixed=TRUE)
  # make plot
  curr.GROBS <- llply(unique(curr.FPLY$d), function(x) {
    ggplot() +
      geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
        fill='grey85', color='grey70') +
      geom_polygon(data=filter(curr.FPLY, d==x), aes_string(x='long', y='lat',
        group='group', fill='value'), color='grey10') +
      theme_classic() +
      theme(
        axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
        panel.border=element_rect(color='black', fill=NA, size=1),
        strip.background = element_rect(fill='grey20'), strip.text = element_text(color='white', size=20)
      ) +
      coord_cartesian(
        xlim=buffered.range(grid.FPLY$long, 0),
        ylim=buffered.range(grid.FPLY$lat, 0)
      ) +
      scale_fill_gradientn(name='',
        colors=brewer.pal(9, 'RdYlBu'),
        guide=guide_colorbar(ticks=element_line(color='black'),
          border=element_line(color='black'), barheight=unit(3.0, 'cm')),
        labels=function(x) {formatC(x, format='f', digits=2)}
      ) + facet_wrap(~d)
  })
  do.call(grid.arrange, append(curr.GROBS, list(ncol=3)))
  invisible()
}

@@

```{r, echo=FALSE, fig.width=calc.fig.width(1), fig.height=calc.fig.height(1), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. Each panel shows a different dimension of variation as indicated by its title. Squares represent planning units. Samples collected from the species were subject to NMDS to ordinate the main axes of adaptive (if detected) and neutral genetic variation. The bioclimatic data were clipped to planning units where the species was found, and subject to a principal components analysis to summarise the main gradients of environmental variation. The panels show the spatial distribution of the ordinated environmental and genetic data averaged to the planning-unit level. Planning units where individuals were not observed are shown in gray.')}
if (is.speciesPlottable(1)) plot.spp.spaces(1)
```

```{r, echo=FALSE, fig.width=calc.fig.width(2), fig.height=calc.fig.height(2), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(2)) plot.spp.spaces(2)
```

```{r, echo=FALSE, fig.width=calc.fig.width(3), fig.height=calc.fig.height(3), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(3)) plot.spp.spaces(3)
```

```{r, echo=FALSE, fig.width=calc.fig.width(4), fig.height=calc.fig.height(4), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(4)) plot.spp.spaces(4)
```

```{r, echo=FALSE, fig.width=calc.fig.width(5), fig.height=calc.fig.height(5), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(5)) plot.spp.spaces(5)
```

```{r, echo=FALSE, fig.width=calc.fig.width(6), fig.height=calc.fig.height(6), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(6)) plot.spp.spaces(6)
```

```{r, echo=FALSE, fig.width=calc.fig.width(7), fig.height=calc.fig.height(7), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(7)) plot.spp.spaces(7)
```

```{r, echo=FALSE, fig.width=calc.fig.width(8), fig.height=calc.fig.height(8), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(8)) plot.spp.spaces(8)
```

```{r, echo=FALSE, fig.width=calc.fig.width(9), fig.height=calc.fig.height(9), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(9)) plot.spp.spaces(9)
```

```{r, echo=FALSE, fig.width=calc.fig.width(10), fig.height=calc.fig.height(10), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(10)) plot.spp.spaces(10)
```

```{r, echo=FALSE, fig.width=calc.fig.width(11), fig.height=calc.fig.height(11), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(11)) plot.spp.spaces(11)
```

```{r, echo=FALSE, fig.width=calc.fig.width(12), fig.height=calc.fig.height(12), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(12)) plot.spp.spaces(12)
```

```{r, echo=FALSE, fig.width=calc.fig.width(13), fig.height=calc.fig.height(13), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(13)) plot.spp.spaces(13)
```

```{r, echo=FALSE, fig.width=calc.fig.width(14), fig.height=calc.fig.height(14), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(14)) plot.spp.spaces(14)
```

```{r, echo=FALSE, fig.width=calc.fig.width(15), fig.height=calc.fig.height(15), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(15)) plot.spp.spaces(15)
```

```{r, echo=FALSE, fig.width=calc.fig.width(16), fig.height=calc.fig.height(16), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(16)) plot.spp.spaces(16)
```

```{r, echo=FALSE, fig.width=calc.fig.width(17), fig.height=calc.fig.height(17), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(17)) plot.spp.spaces(17)
```

```{r, echo=FALSE, fig.width=calc.fig.width(18), fig.height=calc.fig.height(18), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(18)) plot.spp.spaces(18)
```

```{r, echo=FALSE, fig.width=calc.fig.width(19), fig.height=calc.fig.height(19), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(19)) plot.spp.spaces(19)
```

```{r, echo=FALSE, fig.width=calc.fig.width(20), fig.height=calc.fig.height(20), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(20)) plot.spp.spaces(20)
```

```{r, echo=FALSE, fig.width=calc.fig.width(21), fig.height=calc.fig.height(21), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(21)) plot.spp.spaces(21)
```

```{r, echo=FALSE, fig.width=calc.fig.width(22), fig.height=calc.fig.height(22), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(22)) plot.spp.spaces(22)
```

```{r, echo=FALSE, fig.width=calc.fig.width(23), fig.height=calc.fig.height(23), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(23)) plot.spp.spaces(23)
```

```{r, echo=FALSE, fig.width=calc.fig.width(24), fig.height=calc.fig.height(24), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(24)) plot.spp.spaces(24)
```

```{r, echo=FALSE, fig.width=calc.fig.width(25), fig.height=calc.fig.height(25), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(25)) plot.spp.spaces(25)
```

```{r, echo=FALSE, fig.width=calc.fig.width(26), fig.height=calc.fig.height(26), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(26)) plot.spp.spaces(26)
```

```{r, echo=FALSE, fig.width=calc.fig.width(27), fig.height=calc.fig.height(27), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}, and the distribution of its adaptive and neutral genetic variation in the study area. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(27)) plot.spp.spaces(27)
```

@@

# make maps
ggplot() +
  geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
    fill='grey85', color='grey70') +
  geom_polygon(data=grid.sub.FPLY, aes_string(x='long', y='lat',
    group='group', fill='Selection.Frequency'),
    alpha=0.8, color=NA) +
  theme_classic() +
  theme(axis.ticks=element_blank(), axis.text=element_blank(),
    plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank(),
    strip.background = element_rect(fill='grey20'),
    strip.text = element_text(color='white', size=8),
    legend.position='bottom', legend.key.width=unit(1.8, 'cm'),
    legend.title=element_text(vjust=-5),
    legend.margin=unit(c(0.1), 'cm'),
    axis.title=element_blank()) +
  coord_cartesian(
    xlim=buffered.range(grid.sub.FPLY$long, 0),
    ylim=buffered.range(grid.sub.FPLY$lat, 0)
  ) +
  facet_grid(Context ~ Prioritization) +
  scale_fill_gradient(name='Selection Frequency (%)',
    guide=guide_colorbar(title.position='bottom', title.hjust=0.5,
      ticks=element_line(color='black'), border=element_line(color='black'))
  )
```

```{r, echo=FALSE, fig.width=9.5, fig.height=10, out.width='7.5in', out.height='8.5in', fig.cap=paste0('Species distributions. Squares represent planning units. For a given species, planning units that it was found in are shown in bright blue.')}
## plot map of species distributions
# fortify data
spp.grid.FPLY <- ldply(unique(spp.samples.DF$species), function(x) {
    z <- grid.FPLY[,c('long', 'lat', 'group', x),drop=FALSE]
    names(z)[4] <- 'presence'
    z$species <- gsub('\\_', ' ', x)
    return(z)
  }
) %>% mutate(presence=factor(c('absent', 'present')[presence+1]))

# plot species data
ggplot() +
  geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
    fill='grey85', color='grey70') +
  geom_polygon(data=spp.grid.FPLY, aes(x=long, y=lat,
    group=group, fill=presence), alpha=0.8, color='grey10') +
  theme_classic() +
  theme(
    axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
    strip.background = element_rect(fill='grey20'),
    strip.text = element_text(color='white', face='italic'),
    axis.title=element_blank()
  ) +
    scale_fill_manual(name='Occupancy', values=c('absent'='#FC8D59', 'present'='#91CF60')) +
  coord_cartesian(
    xlim=buffered.range(grid.FPLY$long, 0),
    ylim=buffered.range(grid.FPLY$lat, 0)
  ) +
  facet_wrap(~ species, ncol=4)
```

@@

  node[shape = ellipse, style = filled, color = darkslategray, fillcolor = white]
  calc_geo_as [label = 'Processing\n(Figure S60)']
  calc_env_as [label = 'Processing\n(Figure S61)']
  calc_genetic_as [label = 'Processing\n(Figure S62)']

@@

      fill='grey85', color='grey75') +

@@

@@

    # create pie chart for individual

@@

>>>>

```{r, echo=FALSE, include=FALSE}
plot.spp.spaces <- function(i) {
  ## prepare data
  # get vector of adaptive and neutral column names
  adapt.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_adaptive_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  neutral.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_neutral_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  env.col <- grep(
    paste0(unique(spp.samples.DF$species)[i], '_env_d'),
    names(grid.FPLY), value=TRUE, fixed=TRUE
  )
  # skip species if not used in analysis
  curr.FPLY <- grid.FPLY %>%
    select(one_of(adapt.col, neutral.col, env.col), group, long, lat) %>%
    mutate_each(funs(unname), one_of(adapt.col, neutral.col, env.col)) %>%
    filter(!is.na(.[[1]])) %>%
    gather(d, value, contains('adaptive'), contains('neutral'), contains('env')) %>%
    mutate(d=as.character(d)) %>%
    mutate(d=gsub(paste0(unique(spp.samples.DF$species)[i], '_'), '', d, fixed=TRUE)) %>%
    mutate(d=gsub('_', ' ', d, fixed=TRUE)) %>%
    mutate(d=gsub('env', 'environmental', d, fixed=TRUE))
  for (j in seq_len(max(length(adapt.col),length(neutral.col),length(env.col))))
    curr.FPLY$d <- gsub(paste0('d', as.character(j)), paste0('(', j, ')'), curr.FPLY$d, fixed=TRUE)
  # make plot
  curr.GROBS <- llply(unique(curr.FPLY$d), function(x) {
    ggplot() +
      geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
        fill='grey85', color='grey70', size=0.01) +
      geom_polygon(data=filter(curr.FPLY, d==x), aes_string(x='long', y='lat',
        group='group', fill='value'), color='grey10') +
      theme_classic() +
      theme(
        axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
        panel.border=element_rect(color='black', fill=NA, size=1),
        strip.background = element_rect(fill='grey20'), strip.text = element_text(color='white', size=20)
      ) +
      coord_cartesian(
        xlim=buffered.range(grid.FPLY$long, 0),
        ylim=buffered.range(grid.FPLY$lat, 0)
      ) +
      scale_fill_gradientn(name='',
        colors=brewer.pal(9, 'RdYlBu'),
        guide=guide_colorbar(ticks=element_line(color='black'),
          border=element_line(color='black'), barheight=unit(3.0, 'cm')),
        labels=function(x) {formatC(x, format='f', digits=2)}
      ) + facet_wrap(~d)
  })
  do.call(grid.arrange, append(curr.GROBS, list(ncol=3)))
  invisible()
}

@@

```{r, echo=FALSE, fig.width=calc.fig.width(1), fig.height=calc.fig.height(1), fig.cap=paste0('Distribution of environmental variation found across the geographic range of \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}, and the distribution of its adaptive (if detected) and neutral genetic variation in the study area. Each panel shows a different dimension of variation as indicated by its title. Squares represent planning units. Samples collected from the species were subject to NMDS to ordinate the main axes of adaptive (if detected) and neutral genetic variation. The bioclimatic data were clipped to planning units where the species was found, and subject to a principal components analysis to summarise the main gradients of environmental variation. The panels show the spatial distribution of the ordinated environmental and genetic data averaged to the planning-unit level. Planning units where individuals were not observed are shown in gray.')}
if (is.speciesPlottable(1)) plot.spp.spaces(1)
```

```{r, echo=FALSE, fig.width=calc.fig.width(2), fig.height=calc.fig.height(2), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(2)) plot.spp.spaces(2)
```

```{r, echo=FALSE, fig.width=calc.fig.width(3), fig.height=calc.fig.height(3), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(3)) plot.spp.spaces(3)
```

```{r, echo=FALSE, fig.width=calc.fig.width(4), fig.height=calc.fig.height(4), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(4)) plot.spp.spaces(4)
```

```{r, echo=FALSE, fig.width=calc.fig.width(5), fig.height=calc.fig.height(5), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(5)) plot.spp.spaces(5)
```

```{r, echo=FALSE, fig.width=calc.fig.width(6), fig.height=calc.fig.height(6), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(6)) plot.spp.spaces(6)
```

```{r, echo=FALSE, fig.width=calc.fig.width(7), fig.height=calc.fig.height(7), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(7)) plot.spp.spaces(7)
```

```{r, echo=FALSE, fig.width=calc.fig.width(8), fig.height=calc.fig.height(8), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(8)) plot.spp.spaces(8)
```

```{r, echo=FALSE, fig.width=calc.fig.width(9), fig.height=calc.fig.height(9), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(9)) plot.spp.spaces(9)
```

```{r, echo=FALSE, fig.width=calc.fig.width(10), fig.height=calc.fig.height(10), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(10)) plot.spp.spaces(10)
```

```{r, echo=FALSE, fig.width=calc.fig.width(11), fig.height=calc.fig.height(11), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(11)) plot.spp.spaces(11)
```

```{r, echo=FALSE, fig.width=calc.fig.width(12), fig.height=calc.fig.height(12), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(12)) plot.spp.spaces(12)
```

```{r, echo=FALSE, fig.width=calc.fig.width(13), fig.height=calc.fig.height(13), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(13)) plot.spp.spaces(13)
```

```{r, echo=FALSE, fig.width=calc.fig.width(14), fig.height=calc.fig.height(14), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(14)) plot.spp.spaces(14)
```

```{r, echo=FALSE, fig.width=calc.fig.width(15), fig.height=calc.fig.height(15), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(15)) plot.spp.spaces(15)
```

```{r, echo=FALSE, fig.width=calc.fig.width(16), fig.height=calc.fig.height(16), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(16)) plot.spp.spaces(16)
```

```{r, echo=FALSE, fig.width=calc.fig.width(17), fig.height=calc.fig.height(17), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(17)) plot.spp.spaces(17)
```

```{r, echo=FALSE, fig.width=calc.fig.width(18), fig.height=calc.fig.height(18), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(18)) plot.spp.spaces(18)
```

```{r, echo=FALSE, fig.width=calc.fig.width(19), fig.height=calc.fig.height(19), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(19)) plot.spp.spaces(19)
```

```{r, echo=FALSE, fig.width=calc.fig.width(20), fig.height=calc.fig.height(20), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(20)) plot.spp.spaces(20)
```

```{r, echo=FALSE, fig.width=calc.fig.width(21), fig.height=calc.fig.height(21), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(21)) plot.spp.spaces(21)
```

```{r, echo=FALSE, fig.width=calc.fig.width(22), fig.height=calc.fig.height(22), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(22)) plot.spp.spaces(22)
```

```{r, echo=FALSE, fig.width=calc.fig.width(23), fig.height=calc.fig.height(23), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(23)) plot.spp.spaces(23)
```

```{r, echo=FALSE, fig.width=calc.fig.width(24), fig.height=calc.fig.height(24), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(24)) plot.spp.spaces(24)
```

```{r, echo=FALSE, fig.width=calc.fig.width(25), fig.height=calc.fig.height(25), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(25)) plot.spp.spaces(25)
```

```{r, echo=FALSE, fig.width=calc.fig.width(26), fig.height=calc.fig.height(26), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(26)) plot.spp.spaces(26)
```

```{r, echo=FALSE, fig.width=calc.fig.width(27), fig.height=calc.fig.height(27), fig.cap=paste0('Distribution of intra-specific variation for \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S1 caption for conventions.')}
if (is.speciesPlottable(27)) plot.spp.spaces(27)
```

@@

# make maps
ggplot() +
  geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
    fill='grey85', color='grey70', size=0.01) +
  geom_polygon(data=grid.sub.FPLY, aes_string(x='long', y='lat',
    group='group', fill='Selection.Frequency'),
    alpha=0.8, color=NA) +
  theme_classic() +
  theme(axis.ticks=element_blank(), axis.text=element_blank(),
    plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank(),
    strip.background = element_rect(fill='grey20'),
    strip.text = element_text(color='white', size=8),
    legend.position='bottom', legend.key.width=unit(1.8, 'cm'),
    legend.title=element_text(vjust=-5),
    legend.margin=unit(c(0.1), 'cm'),
    axis.title=element_blank()) +
  coord_cartesian(
    xlim=buffered.range(grid.sub.FPLY$long, 0),
    ylim=buffered.range(grid.sub.FPLY$lat, 0)
  ) +
  facet_grid(Context ~ Prioritization) +
  scale_fill_gradient(name='Selection Frequency (%)',
    guide=guide_colorbar(title.position='bottom', title.hjust=0.5,
      ticks=element_line(color='black'), border=element_line(color='black'))
  )
```

```{r, echo=FALSE, fig.width=9.5, fig.height=10, out.width='7.5in', out.height='8.5in', fig.cap=paste0('Species distributions. Squares represent planning units. For a given species, planning units that it was found in are shown in green.')}
## plot map of species distributions
# fortify data
spp.grid.FPLY <- ldply(unique(spp.samples.DF$species), function(x) {
    z <- grid.FPLY[,c('long', 'lat', 'group', x),drop=FALSE]
    names(z)[4] <- 'presence'
    z$species <- gsub('\\_', ' ', x)
    return(z)
  }
) %>% mutate(presence=factor(c('absent', 'present')[presence+1]))

# plot species data
ggplot() +
  geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
    fill='grey85', color='grey70', size=0.01) +
  geom_polygon(data=spp.grid.FPLY, aes(x=long, y=lat,
    group=group, fill=presence), alpha=0.8, color='grey10') +
  theme_classic() +
  theme(
    axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
    strip.background = element_rect(fill='grey20'),
    strip.text = element_text(color='white', face='italic'),
    axis.title=element_blank()
  ) +
    scale_fill_manual(name='Occupancy', values=c('absent'='#FC8D59', 'present'='#91CF60')) +
  coord_cartesian(
    xlim=buffered.range(grid.FPLY$long, 0),
    ylim=buffered.range(grid.FPLY$lat, 0)
  ) +
  facet_wrap(~ species, ncol=4)
```

@@

  node[shape = ellipse, style = filled, color = darkslategray, fillcolor = white]
  calc_geo_as [label = 'Processing\n(Figure S33)']
  calc_env_as [label = 'Processing\n(Figure S34)']
  calc_genetic_as [label = 'Processing\n(Figure S35)']

@@

      fill='grey85', color='grey75', size=0.01) +

@@

  # define colors for species
  spp.cols <- legend.CHR[seq_len(n_distinct(curr.spp.DF$Population))]
  names(spp.cols) <- as.character(unique(curr.spp.DF$Population))

@@

@@

        values=spp.cols
